Verifying Demonstrations

### 2019-07-16 paper/current-crowd-counting.tex
Breaks up related work from crowd counting methods

The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
Clearly, this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where the they were taken).
However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
For instance, there is a risk that participants are recognizable from the material if they do not wear masks.

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd on a selected area.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
This is similar to the method usually used by police (\eg during the protests in Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would fill a space of 3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \citet{NNCrowdCounting}).
This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
They are generally based on machine learning techniques, and thus also require a training dataset to work.
In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but still this might be difficult. 
Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
In addition, it is difficult (if not impossible) to avoid to count some people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).

Another problem for all the above methods is exemplified by the demonstrations in Seoul:
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he demonstrators not only gather in open space, but also small alleys and between buildings%
}.
In this situation it is very difficult to faithfully capture the situation.
Indeed, even if the scene is taken from different angles, there is the additional problem of not counting people twice.

During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
However, in order to work this method makes many additional assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
The company presumed that about half of smartphone users usually leave on their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
It also assumed that about 20\% of the smartphone signals were repetition from the same device.
}
This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
In addition, as MAC address randomization is now getting a wider adoption precisely to fight physical tracking, this method will not work any more, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.

A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, as many bystanders will also be counted.
Thus, it will not be possible to distinguish clearly between the protesters and the counter-protesters.
Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI number will not be transmitted anymore in plaintext. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in relation to the protest.

@@

In general for all of the above methods, the more a crowd spreads out, the more difficult it is to determine its size.
In particular, one of the challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulties capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting more than once (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.

>>>>

\section{Current crowd counting methods}%
\label{current-crowd-counting}

The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count. Using pictures makes it difficult to get cumulative counts, verify that the pictures have not been manipulated, and to have both privacy and individual verifiability: either one is included in the picture (privacy problem) or not (verifiability problem). Similar limitations exist for estimating the number of persons in a picture or video (\eg the work of \cite{NNCrowdCounting} or  CrowdSize~\cite{CrowdSize}).

Another problem for all the above methods is exemplified by the demonstrations in Seoul:
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he demonstrators not only gather in open space, but also small alleys and between buildings%
}.
In this situation it is very difficult to faithfully capture the situation.
Taking pictures from different angles risks double counts. Another challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.

Counting MAC addresses, as done by a company during the protests in Seoul~\cite{2016DemonstrationsInSeoul} suffers from MAC randomization, though some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough} or using \emph{IMSI catchers}; none of which is verifiable.

@@

CrowdCount \citet{CrowdCount} is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants and thus does not suit an adversarial setting.

### 2019-07-16 paper/intro.tex
Breaks up related work from crowd counting methods

Existing methods for crowd-counting vary significantly in terms of approaches.% (we will review them in detail in \cref{related-work}).
Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.  In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

@@

% The paper is organized as follows.
% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}). Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}). 
% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).

The paper is organized as follows.
In \Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting, followed by a discussion of related work in \cref{related-work}. In \Cref{definitions}, we formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give 
the relevant background on the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.

>>>>

Existing methods for crowd-counting vary significantly in terms of approaches.% (we will review them in detail in \cref{current-crowd-counting}).
Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.  In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

@@

% The paper is organized as follows.
% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}). Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{current-crowd-counting}). 
% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).

The paper is organized as follows.
In \Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting, followed by a discussion of current 
crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
we formalize the notion of protest and the desired verifiability and privacy 
properties, and in \cref{building-blocks}, we give the relevant background on 
the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
We compare it to related work in \cref{related-work}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.
